---
title: "2020_44_Canadian_Wind_Turbines"
author: "Eric Fletcher"
date: "10/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

The data for today's post comes from the [[Government of Canada](%5Bhttps://open.canada.ca/data/en/dataset/79fdad93-9025-49ad-ba16-c26d718cc070)]([<https://open.canada.ca/data/en/dataset/79fdad93-9025-49ad-ba16-c26d718cc070>](https://open.canada.ca/data/en/dataset/79fdad93-9025-49ad-ba16-c26d718cc070){.uri}) accessed via the [TidyTuesday](<https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-10-27/readme.md>) project.

According to their website:

> The Canadian Wind Turbine Database contains the geographic location and key technology details for wind turbines installed in Canada.
>
> This dataset was jointly compiled by researchers at CanmetENERGY-Ottawa and by the Centre for Applied Business Research in Energy and the Environment at the University of Alberta, under contract from Natural Resources Canada.

## Data Dictionary:

| Variable                    | Description                      |
|:----------------------------|:---------------------------------|
| objectid                    | Unique ID                        |
| province_territory          | Province/territory               |
| project_name                | Project name                     |
| total_project_capacity_mw   | Electrical capacity in megawatts |
| turbine_identifier          | Turbine ID                       |
| turbine_number_in_project   | Turbine number in project        |
| turbine_rated_capacity_k\_w | Turbine capacity in kilowatts    |
| rotor_diameter_m            | Rotor diameter in meters         |
| hub_height_m                | Hub height in meters             |
| manufacturer                | Manufacturer                     |
| model                       | Model ID                         |
| commissioning_date          | Commission date                  |
| latitude                    | Latitude                         |
| longitude                   | Longitude                        |
| notes                       | Notes about the data             |

## Data Exploration:

### Data and library Import

```{r}
library(tidytuesdayR)
library(tidyverse)
library(rnaturalearth)
library(rnaturalearthhires)
library(rgeos)
# Use this to install rnaturalearthhires which is An R package to store data for the rnaturalearth package.
devtools::install_github("ropensci/rnaturalearthhires")
library(sf)
library(scales)
```

```{r}
# Import the data.
wind_turbine <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-10-27/wind-turbine.csv')

```

```{r}
wind_turbine %>% 
  view()

wind_turbine %>% 
  count(project_name, sort = TRUE)
```

```{r}
# Return Canada polygons using `ne_states`
canada <- ne_states(country = "Canada", returnclass = "sf")
 

```

```{r}
# A single location for every project. 
wind_projects_processed <- wind_turbine %>% 
  # If turbine capacity is less than 0, replace with NA, else return the turbine capacity.
  mutate(turbine_rated_capacity_k_w = ifelse(turbine_rated_capacity_k_w < 0, NA,
                                             turbine_rated_capacity_k_w)) %>% 
  group_by(project_name, province_territory) %>% 
  summarize(year = min(commissioning_date, na.rm = TRUE),
            turbines = n(),
            total_capacity = sum(turbine_rated_capacity_k_w),
            lon = mean(longitude),
            lat = mean(latitude),
            # Determine how spread out each project is.
            # Lower the sd the less spread out the project it.
            # Higher the sd the more spread out the project is.
            long_sd = sd(longitude),
            lat_sd = sd(latitude)) %>% 
  mutate(year = as.numeric(year))

# Convert foreign object to an sf object to be used in geom_sf
wind_projects_sf <- st_as_sf(wind_projects_processed, coords = c("lon", "lat"))

# Retrieve the coordinate reference system from the sf object above. 
st_crs(wind_projects_sf) <- 4326

# Plot 
ggplot() +
  geom_sf(data = canada, mapping = aes(geometry = geometry)) +
  geom_sf(
    data = wind_projects_sf,
    mapping = aes(size = turbines, color = total_capacity)
  ) +
  # Applying a modification to geom_sf to use a different projection of the map.
  # Canada Albers Equal Area Conic (https://epsg.io/102001)
  coord_sf(crs = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-96 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs") +
        theme_void()

?coord_sf

```

```{r}
options(scipen = 999)

# Determine if projects cover multiple years. 
wind_turbine %>% 
  distinct(project_name, commissioning_date) %>% 
  count(project_name, sort = TRUE)


# Distribution of project commissioning date.
wind_projects_processed %>% 
  ggplot(aes(year)) +
  geom_histogram()

# How has turbine capacity changed over time? 
wind_projects_processed %>% 
  ggplot(aes(year, total_capacity)) +
  geom_point() +
  scale_y_continuous(label = comma)

# How has individual turbine capacity changed over time?
wind_projects_processed %>% 
  ggplot(aes(year, total_capacity / turbines)) +
  geom_point() +
  scale_y_continuous(label = comma)

# What is the turbine capacity for each model?
# Some models have multiple capacities. Is there a reason for this?
# Best bet is to take the median since there are cases where most are 1 value but sometimes another.
wind_projects %>% 
  group_by(model) %>% 
  summarize(turbine_rated_capacity_k_w = n_distinct(turbine_rated_capacity_k_w)) %>% 
  arrange(desc(turbine_rated_capacity_k_w))

wind_projects %>% 
  group_by(model, hub_height_m) %>%
  summarize(total_project_capacity_mw = median(total_project_capacity_mw),
            turbine_rated_capacity_k_w = median(turbine_rated_capacity_k_w),
            turbines = n(),
            projects = n_distinct(project_name)) %>% 
  arrange(desc(projects)) %>% 
  # Does bigger hub height lead to larger capacity? (Yes!)
  ggplot(aes(turbine_rated_capacity_k_w, hub_height_m)) +
  geom_point()

  
```
